---
title: "Assignment 2"
author: "Muhammed Taha Yilmaz"
date: "17 01 2022"
output: word_document
---
```{r include=FALSE}
library(tidyverse)
set.seed(2017556069)
library(knitr)
```

# Assignment 2 Part 1

```{r include=FALSE}
mydata <- read_csv2("C:/Users/mtaha/desktop/covid-data-20200.csv")
my_data<-mydata[sample(nrow(mydata), 1000),]
my_data
```
## Q1 : Calculate the five-number summary statistics (minimum-Q1-median-Q3-maximum) of covid-19 daily new cases for each country within each month. (you can use quantile() function to get the quartiles)
```{r echo=FALSE, message=FALSE, warning=FALSE}
answer1 <- my_data %>% group_by(location, month) %>% 
  summarize(
    min = min(new_cases,na.rm = TRUE),
    Q1 = quantile(new_cases, 0.25,na.rm = TRUE),
    Q2 = quantile(new_cases, 0.50,na.rm = TRUE),
    Q3 = quantile(new_cases, 0.75,na.rm = TRUE),
    max = max(new_cases,na.rm = TRUE)
    )
kable(head(answer1,10))
```
## Q2 : Find the highest daily cases and deaths separately for each country. 
```{r echo=FALSE, message=FALSE, warning=FALSE}
answer2 <- my_data %>% group_by(location) %>%
  summarize(
    max_case = max(new_cases), 
    max_death = max(new_deaths, na.rm = TRUE)
    )
answer2 <- arrange(answer2,desc(max_case))
kable(head(answer2,10))
```
## Q3 : Identify the month in which the mean daily cases is the highest for each country.
```{r echo=FALSE, message=FALSE, warning=FALSE}
answer3 <- my_data %>% group_by(location,month) %>%
  summarize(
    Mean_of_dailycases = mean(new_cases, na.rm=TRUE)
  )
answer3 <-filter(answer3, Mean_of_dailycases == max(Mean_of_dailycases))
kable(head(answer3,10))
```
## Q4 : Select 3 country and plot the distribution of daily cases by month. Use location as clusters (i.e., color=location) to show the difference between countries.
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.cap='Figure 1. The Distribution of daily cases by chosen location(United Kingdom","Italy","Switzerland").'}
ggplot(data=filter(my_data, location %in% c("United Kingdom","Italy","Switzerland"))) +
  geom_boxplot(mapping=aes(x=as.factor(month), y=new_cases, color=location))
```


# Assignment 2 Part 2

```{r include=FALSE, message=FALSE, warning=FALSE}
words1 <- sample(sentences,100)
words2 <-str_split(words1,boundary("word")) %>%
  simplify()
words2 <- unique(words2)
```

## Q1 : Find words which are starting with “a” and ending with “e”.
```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(words2[str_detect(words2,"^a.+e$")])
```

## Q2 : Calculate the number of words which have more than 3 vowels.
```{r echo=FALSE, message=FALSE, warning=FALSE}
sum(str_count(words2,"[aeiou]")>3)
kable(words2[str_count(words2,"[aeiou]")>3])
```

## Q3 : List the five longest word in your data
```{r echo=FALSE, message=FALSE, warning=FALSE}
new_data <- tibble(words2, longest=(str_length(words2)))
long <- arrange(new_data,desc(longest))
kable(head(long,5))
```

## Q4 : Try to find word(s) which contain any of these words: age, any, day, exp, her, pro, the.
```{r echo=FALSE, message=FALSE, warning=FALSE}
find_words<-c("age","any","day","exp","her","pro","the")
find_words2<-str_c(find_words, collapse = "|")
kable(str_subset(words2,find_words2))
```

