---
title: "Assignment 3"
author: "Muhammed Taha Yilmaz"
date: "17 01 2022"
output: word_document
---
```{r include=FALSE}
library(tidyverse)
set.seed(2017556069)
library(knitr)
```

## Q1 : Write a function that finds a prime number(s) given a set of numbers. Your function also provides prime factors of non-prime numbers. The function you will write should return the prime number(s) given in this vector and the non-prime number(s) with their prime factors.
```{r echo=FALSE, message=FALSE, warning=FALSE}
ty_func1<-function() {
  nums<-c(89,107,597,931,1083)
  i<-2
  prime<-c()
  non_prime<-c()
  
  for(x in nums) {
    if (x == 2) {
      prime<-c(prime,x)
    } else if (any(x %% 2:(x-1) == 0)) {
      non_prime<-c(non_prime,x)
      non_prime <- c(non_prime, paste0("["))
      while(x >= i){
        if(! x %% i) {
          non_prime <- c(non_prime, i)
          x <- x/i
          i <- i - 1
        }
        i <- i + 1
      }
      non_prime <- c(non_prime, paste0("]"))
      i<-2
    }
    else {
      prime<-c(prime,x)  }
  }
  cat("Prime numbers:", prime, "\n")
  cat("Non-prime numbers:", non_prime)
}
ty_func1()
```

## Q2 : Write a function that finds the letter numbers of all words in a given text and sorts the text according to those numbers from words with few letters to words with many letters. Sort the words containing the same number of letters alphabetically.
```{r echo=FALSE, message=FALSE, warning=FALSE}
ty_func2<-function(){
  words1 <- sample(sentences,6)
  words2 <-str_split(words1,boundary("word")) %>%
    simplify()
  words2<-tolower(words2)
  ty<-str_sort(words2)
  ty2<-ty[order(str_count(ty,"."))]
  ty3<-str_c(ty2, collapse =" ")
  kable(ty3)
}
ty_func2()
```